Bayesian Sparsification of Deep $\cplx$-valued networks

### 2020-03-21 paper/paper.tex
thorough proofread 5 (intro to sec 5) * compactified the intro, moved compression and fourier fatures into to it

We study the compression-performance trade-off of the proposed Bayesian sparsification
methods for $\cplx$-valued networks presented above on the datasets, that have been
studied in prior research on complex-valued networks.

% setup and common experiment settings
For each dataset we conduct a set of experiments in which we try out all combinations of
model kinds ($\real$ or $\cplx$), sparsification methods (VD or ARD) and input features.
Where reasonable, we also study the effects of halving ($\cplx$) or doubling ($\real$)
of the size of intermediate layers in each network \citep{monning_evaluation_2018}.
%
Each network within every experiment passes through three successive stages of training:
pre-training, sparsification, and fine-tuning (sec.~\ref{sub:fitting_and_sparsification}).
%
Each experiment is replicated \textit{five} times to take into account random initialization,
random order of the mini-batch during SGD, stochastic outputs of the intermediate layers,
and non-determinism of single-precision computations on GPUs.

Unless specified otherwise, every experiment uses global gradient clipping within an
$\ell_2$-norm ball of radius $0.5$, employs SGD with ADAM optimizer with the base learning
rate of $10^{-3}$. We note that since our experiments are on classification tasks,
$\cplx$-valued networks ultimately have to output a real-valued logit score. Following
\citet{wolter_complex_2018} and \citet{trabelsi_deep_2017}, the class scores are taken
as real parts of the $\cplx$ output.

@@

% image features
Since image data is not naturally $\cplx$-valued, we preprocess images by either embedding
$\real$-data into $\cplx$ assuming $\Re z = 0$ (\texttt{raw}), or applying the two-dimensional
Fourier Transform (\texttt{fft}), shifting lower frequencies to the centre of the image. We
do not investigate the option, proposed by \citet{trabelsi_deep_2017}, to train an auxiliary
model to synthesize the imaginary component from the real data.

>>>>

We study the compression-performance trade-off of the proposed Bayesian sparsification
method for $\cplx$-valued networks presented above on image classification and music
annotation tasks.
%
Following \citet{wolter_complex_2018} and \citet{trabelsi_deep_2017}, the class logit scores
are taken as real part of the complex-valued output of a network.
%
% image features
Since image data is not naturally $\cplx$-valued, we preprocess it by either embedding
$\real$-data into $\cplx$ assuming $\Im z = 0$ (\texttt{raw}), or applying the two-dimensional
Fourier Transform (\texttt{fft}), shifting lower frequencies to the centre of the image.
We do not investigate the option to train an auxiliary model to synthesize the imaginary
component from the real data, proposed by \citet{trabelsi_deep_2017}.

% setup and common experiment settings
For each dataset we conduct a set of experiments in which we try out all combinations of
model kinds ($\real$ or $\cplx$), sparsification methods (VD or ARD) and input features.
Where reasonable, we also study the effects of halving ($\tfrac12\cplx$) and doubling ($2\real$)
of the size of intermediate layers in each network \citep{monning_evaluation_2018}.
%
Each experiment is replicated \textit{five} times to take into account random initialization,
random order of the mini-batch during SGD, stochastic outputs of the intermediate layers,
and non-determinism of single-precision computations on GPUs.

Each network within every experiment passes through three successive stages of training:
pre-training, sparsification, and fine-tuning (sec.~\ref{sub:fitting_and_sparsification}).
%
Unless specified otherwise, every experiment uses global gradient clipping within an
$\ell_2$-norm ball of radius $0.5$ and uses ADAM optimizer with the base learning rate
of $10^{-3}$.

@@
